quollr: An R Package for Visualizing \(2-D\) Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-08 paper-quollr.Rmd
Updated layouts with same binwidths
paper renders in both html and pdf

---
title: "quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space"
abstract: >
  Non-linear dimension reduction (NLDR) methods provide a low-dimensional representation of high-dimensional data (p\text{-}D) by applying a non-linear transformation. However, the complexity of the transformations and data structures can create wildly different representations depending on the method and (hyper)parameter choices. It is difficult to determine whether any of these representations are accurate, which one is the best, or whether they have missed important structures. The R package \CRANpkg{quollr} has been developed as a new visual tool to determine which method and which (hyper)parameter choices provide the most accurate representation of high-dimensional data. The `triangular_3d_data` data from the \CRANpkg{cardinalR} package is used to illustrate the algorithm and its application within the package.
draft: true
author:  
  - name: Jayani P.G. Lakshika
    affiliation: Monash University
    address: Department of Econometrics and Business Statistics, VIC 3800 Australia
    url: https://jayanilakshika.netlify.app/
    orcid: 0000-0002-6265-6481
    email:  \email{jayani.piyadigamage@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: Department of Econometrics and Business Statistics, VIC 3800 Australia
    url: http://www.dicook.org/
    email: dicook@monash.edu
    orcid: 0000-0002-3813-7155
  - name: Paul Harrison
    affiliation: Monash University
    address: MGBP, BDInstitute, VIC 3800 Australia
    email: paul.harrison@monash.edu
    orcid: 0000-0002-3980-268X
  - name: Michael Lydeamore
    affiliation: Monash University
    address: Department of Econometrics and Business Statistics, VIC 3800 Australia
    email: michael.lydeamore@monash.edu
    orcid: 0000-0001-6515-827X
  - name: Thiyanga S. Talagala
    affiliation: University of Sri Jayewardenepura
    address: Department of Statistics, Gangodawila, Nugegoda 10100 Sri Lanka
    url: https://thiyanga.netlify.app/
    email: ttalagala@sjp.ac.lk
    orcid: 0000-0002-0656-9789
type: package
creative_commons: CC BY
date: "`r Sys.Date()`"
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
output: 
 rjtools::rjournal_web_article:
    css: "style.css"
    keep_md: true
bibliography: RJreferences.bib
editor_options: 
  chunk_output_type: inline
---

@@

```{r}
#| label: tsne-num-bins-limb

@@

```{r}
#| label: prep-limb-tsne-author-model-proj

@@

```{r}
#| label: tsne-best-num-bins-limb

@@

```{r}
#| label: prep-limb-tsne-best-model-proj

@@

```{r}
trimesh_removed_limb + trimesh_removed_limb_best +
  plot_layout(ncol = 3)
```

>>>>

---
title: "quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space"
abstract: >
  Non-linear dimension reduction (NLDR) methods provide a low-dimensional representation of high-dimensional data (p\text{-}D) by applying a non-linear transformation. However, the complexity of the transformations and data structures can create wildly different representations depending on the method and (hyper)parameter choices. It is difficult to determine whether any of these representations are accurate, which one is the best, or whether they have missed important structures. The R package \CRANpkg{quollr} has been developed as a new visual tool to determine which method and which (hyper)parameter choices provide the most accurate representation of high-dimensional data. The `triangular_3d_data` data from the \CRANpkg{cardinalR} package is used to illustrate the algorithm and its application within the package.
draft: true
author:  
  - name: Jayani P.G. Lakshika
    affiliation: Monash University
    address: Department of Econometrics and Business Statistics, VIC 3800 Australia
    url: https://jayanilakshika.netlify.app/
    orcid: 0000-0002-6265-6481
    email:  \email{jayani.piyadigamage@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: Department of Econometrics and Business Statistics, VIC 3800 Australia
    url: http://www.dicook.org/
    email: dicook@monash.edu
    orcid: 0000-0002-3813-7155
  - name: Paul Harrison
    affiliation: Monash University
    address: MGBP, BDInstitute, VIC 3800 Australia
    email: paul.harrison@monash.edu
    orcid: 0000-0002-3980-268X
  - name: Michael Lydeamore
    affiliation: Monash University
    address: Department of Econometrics and Business Statistics, VIC 3800 Australia
    email: michael.lydeamore@monash.edu
    orcid: 0000-0001-6515-827X
  - name: Thiyanga S. Talagala
    affiliation: University of Sri Jayewardenepura
    address: Department of Statistics, Gangodawila, Nugegoda 10100 Sri Lanka
    url: https://thiyanga.netlify.app/
    email: ttalagala@sjp.ac.lk
    orcid: 0000-0002-0656-9789
type: package
creative_commons: CC BY
date: "`r Sys.Date()`"
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
output: 
 rjtools::rjournal_article:
    keep_md: true
bibliography: paper-quollr.bib
editor_options: 
  chunk_output_type: inline
---

@@

```{r}
#| label: tsne-num-bins-limb
#| eval: false

@@

```{r}
#| label: prep-limb-tsne-author-model-proj
#| eval: false

@@

```{r}
#| label: tsne-best-num-bins-limb
#| eval: false

@@

```{r}
#| label: prep-limb-tsne-best-model-proj
#| eval: false

@@

```{r}
#| eval: false
trimesh_removed_limb + trimesh_removed_limb_best +
  plot_layout(ncol = 3)
```

### 2025-04-08 paper-quollr.tex
paper renders in both html and pdf

This paper presents the R package, \texttt{quollr} which introduce a new visual tool in determining which NLDR technique and which (hyper)parameter choice gives most accurate representation of high-dimensional data. The methodology of the algorithm is explained in \emph{cite the methodology paper}. Furthermore, the \texttt{quollr} package enables users to perform hexagonal binning (Carr et al. 2023), resulting in the generation of regular hexagons. The software is available from the Comprehensive R Archive Network (CARN) at \url{https://CRAN.R-project.org/package=quollr}.

@@

\begin{verbatim}
fit_highd_model(
  training_data = s_curve_noise_training,
  emb_df = s_curve_noise_umap_scaled, 
  bin1 = 12, 
  r2 = r2,
  q = 0.07,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = TRUE,
  benchmark_to_rm_lwd_hex = NULL,
  col_start_highd = "x"
  )
\end{verbatim}

\begin{verbatim}
#> $df_bin
#> # A tibble: 37 x 8
#>    hb_id       x1     x2     x3       x4       x5       x6        x7
#>    <int>    <dbl>  <dbl>  <dbl>    <dbl>    <dbl>    <dbl>     <dbl>
#>  1    27 -0.706   1.70   -1.65   0.00918  0.00261 -0.0236  -0.00199 
#>  2    28 -0.214   1.45   -1.98  -0.00966 -0.00370  0.0573   0.000307
#>  3    40  0.356   1.74   -1.89   0.0127  -0.00773 -0.0219  -0.000757
#>  4    50 -0.209   0.453  -1.98   0.0185   0.0189  -0.0999  -0.00412 
#>  5    52  0.00161 1.14   -2.00   0.00206 -0.00940 -0.0974  -0.00796 
#>  6    61 -0.671   0.0922 -1.74  -0.00458  0.0127  -0.0613  -0.00643 
#>  7    62 -0.375   0.328  -1.89  -0.00226 -0.00651 -0.0291   0.00120 
#>  8    74 -0.175   0.0562 -1.98   0.00204 -0.00179  0.0112  -0.00111 
#>  9    75  0.325   0.0821 -1.95   0.00292  0.0197  -0.0165  -0.000881
#> 10   127  0.704   0.454  -0.290 -0.00394  0.0118  -0.00941 -0.00348 
#> # i 27 more rows
#> 
#> $df_bin_centroids
#> # A tibble: 37 x 5
#>    hexID     c_x    c_y std_counts drop_empty
#>    <int>   <dbl>  <dbl>      <dbl> <lgl>     
#>  1    27  0.127  0.0295        1   FALSE     
#>  2    28  0.226  0.0295        0.2 FALSE     
#>  3    40  0.275  0.115         0.6 FALSE     
#>  4    50  0.0287 0.200         0.2 FALSE     
#>  5    52  0.226  0.200         0.2 FALSE     
#>  6    61 -0.0207 0.286         0.2 FALSE     
#>  7    62  0.0780 0.286         0.8 FALSE     
#>  8    74  0.0287 0.371         0.4 FALSE     
#>  9    75  0.127  0.371         0.2 FALSE     
#> 10   127  0.522  0.713         0.4 FALSE     
#> # i 27 more rows
\end{verbatim}

@@

\begin{verbatim}
calc_bins_y(
  bin1 = 12, 
  r2 = r2,
  q = 0.07
  )
\end{verbatim}

\begin{verbatim}
#> $bin2
#> [1] 27
#> 
#> $a1
#> [1] 0.09596332
\end{verbatim}

@@

\begin{verbatim}
hex_binning(
  data = s_curve_noise_umap_scaled, 
  bin1 = 12, 
  r2 = r2,
  q = 0.07
  )
\end{verbatim}

\begin{verbatim}
#> $bins
#> [1] 12 27
#> 
#> $start_point
#> [1] -0.070000 -0.141359
#> 
#> $centroids
#> # A tibble: 324 x 3
#>    hexID     c_x    c_y
#>    <int>   <dbl>  <dbl>
#>  1     1 -0.07   -0.141
#>  2     2  0.0287 -0.141
#>  3     3  0.127  -0.141
#>  4     4  0.226  -0.141
#>  5     5  0.325  -0.141
#>  6     6  0.423  -0.141
#>  7     7  0.522  -0.141
#>  8     8  0.621  -0.141
#>  9     9  0.719  -0.141
#> 10    10  0.818  -0.141
#> # i 314 more rows
#> 
#> $hex_poly
#> # A tibble: 1,944 x 3
#>    hex_poly_id       x       y
#>          <int>   <dbl>   <dbl>
#>  1           1 -0.07   -0.0860
#>  2           1 -0.118  -0.114 
#>  3           1 -0.118  -0.169 
#>  4           1 -0.07   -0.197 
#>  5           1 -0.0220 -0.169 
#>  6           1 -0.0220 -0.114 
#>  7           2  0.0287 -0.0860
#>  8           2 -0.0193 -0.114 
#>  9           2 -0.0193 -0.169 
#> 10           2  0.0287 -0.197 
#> # i 1,934 more rows
#> 
#> $data_hb_id
#> # A tibble: 75 x 4
#>     UMAP1  UMAP2    ID hb_id
#>     <dbl>  <dbl> <int> <int>
#>  1 0.0804 0.320      1    62
#>  2 0.739  1.00       2   165
#>  3 0.840  1.08       3   178
#>  4 0.167  0.0432     4    27
#>  5 0.263  0.398      6    76
#>  6 0.838  2.01       7   310
#>  7 0.734  0.972      8   165
#>  8 0.627  0.721      9   128
#>  9 0.810  1.01      11   178
#> 10 0.903  1.87      12   299
#> # i 65 more rows
#> 
#> $std_cts
#> # A tibble: 45 x 3
#>    hb_id     n std_counts
#>    <int> <int>      <dbl>
#>  1    27     5        1  
#>  2    28     1        0.2
#>  3    38     1        0.2
#>  4    40     3        0.6
#>  5    50     1        0.2
#>  6    52     1        0.2
#>  7    61     1        0.2
#>  8    62     4        0.8
#>  9    64     1        0.2
#> 10    74     2        0.4
#> # i 35 more rows
#> 
#> $tot_bins
#> [1] 324
#> 
#> $non_bins
#> [1] 45
#> 
#> $pts_bins
#> # A tibble: 45 x 2
#>    hexID pts_list    
#>    <int> <named list>
#>  1    62 <int [75]>  
#>  2   165 <int [75]>  
#>  3   178 <int [75]>  
#>  4    27 <int [75]>  
#>  5    76 <int [75]>  
#>  6   310 <int [75]>  
#>  7   128 <int [75]>  
#>  8   299 <int [75]>  
#>  9    74 <int [75]>  
#> 10   287 <int [75]>  
#> # i 35 more rows
#> 
#> attr(,"class")
#> [1] "hex_bin_obj"
\end{verbatim}

@@

df_bin <- avg_highd_data(
  data = df_all, 
  col_start = "x"
  )
\end{verbatim}

@@

\begin{verbatim}
predict_emb(
  test_data = s_curve_noise_training, 
  df_bin_centroids = df_bin_centroids, 
  df_bin = df_bin, 
  type_NLDR = "UMAP"
  )
\end{verbatim}

@@

\begin{verbatim}
glance(
  df_bin_centroids = df_bin_centroids, 
  df_bin = df_bin, 
  training_data = s_curve_noise_training, 
  newdata = NULL, 
  type_NLDR = "UMAP", 
  col_start = "x"
  )
\end{verbatim}

@@

\begin{verbatim}
augment(
  df_bin_centroids = df_bin_centroids, 
  df_bin = df_bin, 
  training_data = s_curve_noise_training, 
  newdata = NULL, 
  type_NLDR = "UMAP", 
  col_start = "x"
  )
\end{verbatim}

@@

\subsection{Tests}\label{tests}

All functions have tests written and implemented using the \CRANpkg{testthat} (Wickham 2011) in R.

These tests illuminated the issues that allowed us to make meaningful changes and understand some pitfalls of the package.

@@

To illustrate the algorithm, we use \(5\text{-}D\) simulated data, which we call the ``triangular\_3d\_data''. This dataset is generated using the \texttt{tri\_3d} function from the \texttt{cardinalR} package. The dataset generation starts with the initialization of a starting point \(p_0 = (x_0, y_0, z_0)\) randomly selected within the \(3\text{-}D\) space using a uniform distribution. Four fixed corner points of a tetrahedron are defined as \(c_1 = (0, 0, 0)\), \(c_2 = (1, 0, 0)\), \(c_3 = (0.5, 1, 0)\), and \(c_4 = (0.5, 0.5, 1)\). For each point \(p_i\) where \(i = 1, 2, \ldots, n\), one of the corner points \(c_j\) (where \(j \in \{1, 2, 3, 4\}\)) is selected randomly, and the new point \(p_i\) is computed as the midpoint between the current point \(p_{i-1}\) and the selected corner point \(c_j\): \(p_i = \frac{p_{i-1} + c_j}{2}\). This iterative process ensures that each new point moves closer to one of the corners, creating a fractal-like triangular distribution of points. The coordinates of each generated point \(p_i\) form the variables \(X_1, X_2, X_3\). The remaining variables \(X_4, X_5\) are all uniform error, with small variance. We would consider \(T=(X_1, X_2, X_3)\) to be the true model.

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1}

\subsection{Deciding an appropriate fit}\label{deciding-an-appropriate-fit}

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-31-1}

\subsection{Fit the appropriate model}\label{fit-the-appropriate-model}

\subsubsection{\texorpdfstring{Construct model in \(2\text{-}D\)}{Construct model in 2\textbackslash text\{-\}D}}\label{construct-model-in-2text-d}

\subsubsection{Selecting parameter values for the model}\label{selecting-parameter-values-for-the-model}

\paragraph{Choice of bins}\label{choice-of-bins}

\paragraph{Removal of low-density bins}\label{removal-of-low-density-bins}

\paragraph{Removing long edges}\label{removing-long-edges}

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-32-1}

\subsubsection{\texorpdfstring{Lifting the model into \(p\text{-}D\)}{Lifting the model into p\textbackslash text\{-\}D}}\label{lifting-the-model-into-ptext-d}

What can I see in high-D?

\begin{itemize}
\tightlist
\item
  Four clusters that are really close
\end{itemize}

What can I see in 2D layout?

\begin{itemize}
\tightlist
\item
  Several clusters (more that what see in high-D)
\end{itemize}

What can learn from the model?

\begin{itemize}
\tightlist
\item
  There are four clusters, but not as the same cluster what data shows. In 2D, the two of actual clusters (high-D clusters) are really close. Also, one of the big high-D cluster is separated to two sub clusters.
\end{itemize}

@@

This article is created using \CRANpkg{knitr} (Xie 2015) and \CRANpkg{rmarkdown} (Xie, Allaire, and Grolemund 2018) in R with the \texttt{rjtools::rjournal\_article} template. The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-dan2023}
Carr, Dan, ported by Nicholas Lewin-Koh, Martin Maechler, and contains copies of lattice functions written by Deepayan Sarkar. 2023. \emph{Hexbin: Hexagonal Binning Routines}. \url{https://CRAN.R-project.org/package=hexbin}.

\bibitem[\citeproctext]{ref-testthat}
Wickham, Hadley. 2011. {``Testthat: Get Started with Testing.''} \emph{The R Journal} 3: 5--10. \url{https://journal.r-project.org/archive/2011-1/RJournal_2011-1_Wickham.pdf}.

\bibitem[\citeproctext]{ref-knitr}
Xie, Yihui. 2015. \emph{Dynamic Documents with {R} and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{https://yihui.name/knitr/}.

\bibitem[\citeproctext]{ref-rmarkdown}
Xie, Yihui, J. J. Allaire, and Garrett Grolemund. 2018. \emph{{R} Markdown: The Definitive Guide}. Boca Raton, Florida: Chapman; Hall/CRC. \url{https://bookdown.org/yihui/rmarkdown}.

\end{CSLReferences}

>>>>

This paper presents the R package, \texttt{quollr} which introduce a new visual tool in determining which Non-linear dimension reduction (NLDR) technique and which (hyper)parameter choice gives most accurate representation of high-dimensional data. The methodology of the algorithm is explained in \emph{cite the methodology paper}. Furthermore, the \texttt{quollr} package enables users to perform hexagonal binning \citep{dan2023}, resulting in the generation of regular hexagons. The software is available from the Comprehensive R Archive Network (CARN) at \url{https://CRAN.R-project.org/package=quollr}.

@@

\begin{verbatim}
fit_highd_model(
  highd_data = s_curve_noise_training,
  nldr_data = s_curve_noise_umap_scaled, 
  bin1 = 12, 
  r2 = r2,
  q = 0.1,
  is_bin_centroid = TRUE
  )
\end{verbatim}

\begin{verbatim}
#> $df_bin
#> # A tibble: 72 x 8
#>    hb_id     x1    x2    x3        x4        x5        x6         x7
#>    <int>  <dbl> <dbl> <dbl>     <dbl>     <dbl>     <dbl>      <dbl>
#>  1    13  0.996  1.77  1.07 -0.0117    0.00979  -0.0725   -0.00321  
#>  2    14  0.829  1.79  1.50 -0.000753 -0.00194  -0.00936  -0.000454 
#>  3    15  0.307  1.78  1.94 -0.00384   0.00212  -0.00117  -0.000159 
#>  4    16 -0.175  1.74  1.98  0.00143   0.00320   0.00450  -0.0000763
#>  5    18 -0.493  1.78  1.87 -0.0100    0.000680  0.0799   -0.000835 
#>  6    26  0.962  1.22  1.22  0.00107  -0.00260  -0.000948  0.000234 
#>  7    27  0.631  1.28  1.75  0.000266  0.00174  -0.00158   0.00114  
#>  8    28  0.139  1.20  1.97 -0.00183   0.000279  0.00177  -0.000666 
#>  9    29 -0.187  1.00  1.98 -0.00228   0.00461  -0.0506   -0.00472  
#> 10    30 -0.562  1.23  1.82 -0.000563  0.00166  -0.00923  -0.000111 
#> # i 62 more rows
#> 
#> $df_bin_centroids
#> # A tibble: 72 x 6
#>    hexID      c_x      c_y bin_counts std_counts drop_empty
#>    <int>    <dbl>    <dbl>      <int>      <dbl> <lgl>     
#>  1    13 -0.0455  0.000514          2     0.0194 FALSE     
#>  2    14  0.0634  0.000514         81     0.786  FALSE     
#>  3    15  0.172   0.000514         56     0.544  FALSE     
#>  4    16  0.281   0.000514         55     0.534  FALSE     
#>  5    18  0.499   0.000514          2     0.0194 FALSE     
#>  6    26  0.00894 0.0949           70     0.680  FALSE     
#>  7    27  0.118   0.0949           78     0.757  FALSE     
#>  8    28  0.227   0.0949           86     0.835  FALSE     
#>  9    29  0.336   0.0949            5     0.0485 FALSE     
#> 10    30  0.445   0.0949           54     0.524  FALSE     
#> # i 62 more rows
\end{verbatim}

@@

\begin{verbatim}
calc_bins_y(
  bin1 = 12, 
  r2 = r2,
  q = 0.1
  )
\end{verbatim}

\begin{verbatim}
#> $bin2
#> [1] 13
#> 
#> $a1
#> [1] 0.1089367
#> 
#> $a2
#> [1] 0.09434198
\end{verbatim}

@@

\begin{verbatim}
hex_binning(
  data = s_curve_noise_umap_scaled, 
  bin1 = 12, 
  r2 = r2,
  q = 0.1
  )
\end{verbatim}

\begin{verbatim}
#> $a1
#> [1] 0.1089367
#> 
#> $a2
#> [1] 0.09434198
#> 
#> $bins
#> [1] 12 13
#> 
#> $start_point
#> [1] -0.10000000 -0.09382762
#> 
#> $centroids
#> # A tibble: 156 x 3
#>    hexID      c_x     c_y
#>    <int>    <dbl>   <dbl>
#>  1     1 -0.1     -0.0938
#>  2     2  0.00894 -0.0938
#>  3     3  0.118   -0.0938
#>  4     4  0.227   -0.0938
#>  5     5  0.336   -0.0938
#>  6     6  0.445   -0.0938
#>  7     7  0.554   -0.0938
#>  8     8  0.663   -0.0938
#>  9     9  0.771   -0.0938
#> 10    10  0.880   -0.0938
#> # i 146 more rows
#> 
#> $hex_poly
#> # A tibble: 936 x 3
#>    hex_poly_id        x       y
#>          <int>    <dbl>   <dbl>
#>  1           1 -0.1     -0.0309
#>  2           1 -0.154   -0.0624
#>  3           1 -0.154   -0.125 
#>  4           1 -0.1     -0.157 
#>  5           1 -0.0455  -0.125 
#>  6           1 -0.0455  -0.0624
#>  7           2  0.00894 -0.0309
#>  8           2 -0.0455  -0.0624
#>  9           2 -0.0455  -0.125 
#> 10           2  0.00894 -0.157 
#> # i 926 more rows
#> 
#> $data_hb_id
#> # A tibble: 3,750 x 4
#>      emb1   emb2    ID hb_id
#>     <dbl>  <dbl> <int> <int>
#>  1 0.276  0.915      1   136
#>  2 0.927  0.347      2    70
#>  3 0.810  0.242      3    45
#>  4 0.137  0.657      5    99
#>  5 0.476  0.799      6   114
#>  6 0.0485 0.0657     7    26
#>  7 0.737  0.851      9   129
#>  8 0.833  0.224     10    45
#>  9 0.909  0.371     11    70
#> 10 0.0890 0.194     12    38
#> # i 3,740 more rows
#> 
#> $std_cts
#> # A tibble: 72 x 3
#>    hb_id     n std_counts
#>    <int> <int>      <dbl>
#>  1    13     2     0.0194
#>  2    14    81     0.786 
#>  3    15    56     0.544 
#>  4    16    55     0.534 
#>  5    18     2     0.0194
#>  6    26    70     0.680 
#>  7    27    78     0.757 
#>  8    28    86     0.835 
#>  9    29     5     0.0485
#> 10    30    54     0.524 
#> # i 62 more rows
#> 
#> $tot_bins
#> [1] 156
#> 
#> $non_bins
#> [1] 72
#> 
#> $pts_bins
#> # A tibble: 72 x 2
#>    hexID pts_list     
#>    <int> <named list> 
#>  1   136 <int [3,750]>
#>  2    70 <int [3,750]>
#>  3    45 <int [3,750]>
#>  4    99 <int [3,750]>
#>  5   114 <int [3,750]>
#>  6    26 <int [3,750]>
#>  7   129 <int [3,750]>
#>  8    38 <int [3,750]>
#>  9   111 <int [3,750]>
#> 10    14 <int [3,750]>
#> # i 62 more rows
#> 
#> attr(,"class")
#> [1] "hex_bin_obj"
\end{verbatim}

@@

df_bin <- avg_highd_data(
  data = df_all
  )
\end{verbatim}

@@

\begin{verbatim}
predict_emb(
  highd_data = s_curve_noise_training, 
  model_2d = df_bin_centroids, 
  model_highd = df_bin
  )
\end{verbatim}

@@

\begin{verbatim}
glance(
  highd_data = s_curve_noise_training, 
  model_2d = df_bin_centroids, 
  model_highd = df_bin
  )
\end{verbatim}

@@

\begin{verbatim}
augment(
  highd_data = s_curve_noise_training, 
  model_2d = df_bin_centroids, 
  model_highd = df_bin
  )
\end{verbatim}

@@

\subsubsection{Link plots}\label{link-plots}

There are mainly two interactive link plots can be generated. \texttt{show\_link\_plots()} helps to examine the fit. The function requires several arguments: points data which contain Non-linear dimension reduction data, high-dimensional data, and high-dimensional model data, and edge data where the from and to links of the edges.

\texttt{show\_error\_link\_plots()} helps to see investigate whether the model fits the points everywhere or fits better in some places, or simply mismatches the pattern. The function requires several arguments: points data which contain Non-linear dimension reduction data, high-dimensional data, high-dimensional model data, and model error, and edge data where the from and to links of the edges.

\begin{verbatim}
show_link_plots(
  point_df = df_exe, 
  edge_df = distance_small_df
  )
\end{verbatim}

\begin{verbatim}
show_error_link_plots(
  point_df = df_exe, 
  edge_df = distance_small_df
  )
\end{verbatim}

--\textgreater{}
--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}
--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

@@

Need to find another application

\url{https://www.nature.com/articles/s41586-018-0590-4\#data-availability}
\url{https://figshare.com/articles/dataset/Robject_files_for_tissues_processed_by_Seurat/5821263/1}

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-limb-mse-1} \end{figure}

@@

This article is created using \CRANpkg{knitr} \citep{knitr} and \CRANpkg{rmarkdown} \citep{rmarkdown} in R with the \texttt{rjtools::rjournal\_article} template. The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}.

\bibliography{paper-quollr.bib}
